---
#word_document: default
title: "In Who's Best Interest? An Empirical Analysis on the Legitimacy of Anti-ESG Legislation"
author: "Omar Vasquez Duque"
date: "2023-03-16"

output: 
  bookdown::pdf_document2:
  
# output:
#   pdf_document: default
#   word_document:
#       reference_docx: docx_template.docx
#   html_document: default
---

# Preliminary Analysis

```{r include=FALSE}

options(scipen=999)

options(digits = 3)
```

```{r include=FALSE}
library(readr)

#setwd("/Users/ovd/Documents/GitHub/esg_pensions")

raw.dfcj <- read_csv("rds_prod.experiment.420656.stacked(18).csv")

table(raw.dfcj$Q10_AGE_WRITE_IN)

```

```{r message=FALSE, warning=FALSE}
library(cregg)
library(janitor)
library(tidyverse)
```

```{r include=FALSE}

dfcj = raw.dfcj %>% 
  clean_names() 

```

```{r include=FALSE}

#'*Check whether it makes sense to filter speeders (if any).*

median_complet_t = median(dfcj$respondent_length_of_interview_seconds) 
# calculate median completion time in secs

dfcj$income_num = readr::parse_number(dfcj$q17_annual_income)

hist(dfcj$respondent_length_of_interview_seconds)

median(dfcj$respondent_length_of_interview_seconds)

434/60

dfcj2 = dfcj %>% 
  filter(respondent_length_of_interview_seconds >= 0.5 * median_complet_t,
         respondent_length_of_interview_seconds <= 2 * median_complet_t) %>% 
  filter(!is.na(income_num)) %>% 
  filter(income_num > 15000)

nrow(dfcj2)/24 #1,617 responses!

dffilt = dfcj %>% 
  filter(income_num < 15000)

nrow(dffilt)/24

dfcj = dfcj %>% 
  mutate(include = ifelse(respondent_length_of_interview_seconds >= 0.5 * median_complet_t & respondent_length_of_interview_seconds <= 2 * median_complet_t & income_num > 15000 & !is.na(income_num), 1, 0))

mean(dfcj$include)

dfcj = dfcj %>% 
  mutate(CONJOINTLY_ACTION = ifelse(include ==1, "INCLUDE_IN_ANALYSIS", "EXCLUDE_FROM_ANALYSIS"))

table(dfcj$CONJOINTLY_ACTION)

dfconjointly = dfcj %>% 
  select(survey_id, CONJOINTLY_ACTION)

#revert
#dfconjointly$CONJOINTLY_ACTION = "INCLUDE_IN_ANALYSIS"


write_csv(dfconjointly, "dfconjointly.csv")
 
 # filter responded too quickly or slowly
```

```{r include=FALSE}
#Transform variables to factors
dfcj = dfcj %>% 
  mutate(expected_pension = factor(expected_pension),
         firearms = factor(invests_in_firearms,
                           levels = c("Invests in firearms", "Does not invest in firearms")),           
         fossil_fuels =  factor(invests_in_fossil_fuels,
                                levels = c("Invests in fossil fuels", "Does not invest in fossil fuels")),
         may_employ_children = factor(invests_in_firms_that_may_employ_children,
                                      levels = c("Invests in firms that may employ children", "Invests in firms that ensure no children are employed")),
         racial_diversity_mgmt = factor(advocates_for_racial_diversity_in_management,
                                   levels = c("Does not advocate for racial diversity in management",
                                              "Advocates for racial diversity in management")),
         gender_equal_pay = factor(advocates_for_equal_pay_for_men_and_women,
                                   levels = c("Does not advocate for equal pay for men and women",
                                              "Advocates for equal pay for men and women")),
        choice_indicator = as.numeric(choice_indicator),
        choice = as.factor(choice_indicator),
        prior = factor(ifelse(q9_taking_into_account_esg_factors_o1_yes ==1, "pro-esg", "anti-esg")),
        republican = factor(ifelse(q11_party_id_o1_republican==1 |
          q12_party_leanings_o1_republican ==1, 1,0)),
        florida = factor(ifelse(q15_state_us_o1_florida==1, 1,0)),
        california = factor(ifelse(q15_state_us_o2_california==1,1,0)),
        age = 2023 - (q10_age_write_in))

```

```{r}
dfcj %>% 
select(invests_in_firms_that_may_employ_children, choice_indicator) %>% 
  table() 

```

Analysis with weighted sample. California = 12.2%; Florida = 6.6% and rest of US = 81.4%.

```{r include=FALSE}

dffl = dfcj %>% 
  filter(florida==1)

dfcl = dfcj %>% 
  filter(california==1)



# Work with weights with a mean of 1
total = nrow(dfcj)

florida.p = nrow(dffl)/total

cali.p = nrow(dfcl)/total

us.p = (total- nrow(dffl) - nrow(dfcl))/total

florida.weight = (6.6/florida.p)/100

cali.weight = (12/cali.p)/100

us.weight = (81.4/us.p)/100
```

```{r include=FALSE}
#Check gender and age 

flfem = dffl %>% 
  filter(q13_gender_o2_female==1)

flfem.n = nrow(flfem)/24

flmale = dffl %>% 
  filter(q13_gender_o1_male==1)

flmale.n = nrow(flmale)/24

```

```{r include=FALSE}
#California

cafem = dfcl %>% 
  filter(q13_gender_o2_female==1)

cafem.n= nrow(cafem)/24

camale = dfcl %>% 
  filter(q13_gender_o1_male==1)

camale.n =nrow(camale)/24

```

```{r include=FALSE}
#U.S.

total_no_filter = nrow(dfcj)/24
  
total_filtered =nrow(dfcj2)/24

usfem = dfcj %>% 
  filter(q15_state_us_o3_other==1,
         q13_gender_o2_female==1) 

usmale = dfcj %>% 
  filter(q15_state_us_o3_other==1,
         q13_gender_o1_male==1)

usfem.n = nrow(usfem)/24

usmale.n = nrow(usmale)/24
  
```

```{r}

dfcj = dfcj %>% 
  mutate(state.weight = case_when(florida==1 ~ florida.weight,
                             california==1 ~ cali.weight,
                             florida == 0 & california == 0 ~us.weight))

#mean(dfcjw$weight) # Looks good
```

The plot below shows the importance of each attribute considering a weighted sample of the U.S. which is representative in terms of age and gender.


```{r echo=FALSE, warning=FALSE}
# weight = dfcjw$weights

mmusw <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "mm", weights = ~ state.weight)

amceusw <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", weights = ~ state.weight)

plot(mmusw, vline = 0.5) + 
  ggtitle("U.S. Weighted Sample")

plot(amceusw, vline = 0) +
  theme_minimal()

summary(amceusw)

ggsave("amceusw.pdf", width = 10, height = 5)

```

Now, apply more comprehensive weights

```{r}

dfcj=dfcj %>% 
  mutate(income = case_when(income_num <=24999 ~ "15,000 to 24,999",
                            income_num >=25000 & income_num <=34999 ~ "25,000 to 34,999",
                            income_num >= 35000 & income_num <=49999 ~  "35,000 to 49,999",
                            income_num >= 50000 & income_num <=74999 ~ "50,000 to 74,999",
                            income_num >= 75000 & income_num <=99999 ~ "75,000 to 99,999",
                            income_num >= 100000 ~ "100,000 or more"))
```

```{r}
table(dfcj$income)
```

```{r}


dfcj = dfcj %>% 
  mutate(gender = case_when(q13_gender_o1_male == 1 ~ "male",
                            q13_gender_o2_female == 1 ~ "female",
                            q13_gender_o3_other == 1 ~ "other"),
         education = case_when(q16_education_o1_some_high_school == 1 ~ "less than hs",
                               q16_education_o2_high_school ==1 ~ "hs",
                               q16_education_o3_some_college ==1 ~ "hs",
                               q16_education_o4_college_degree== 1 ~ "college",
                               q16_education_o5_graduate_degree == 1 ~ "grad school"),
         religiosity =case_when(q18_frequency_o1_0 == 1 ~ "no/low",
                                q18_frequency_o2_1 == 1 ~ "no/low",
                                q18_frequency_o3_2 == 1 ~ "mid",
                                q18_frequency_o4_3 == 1 ~ "mid",
                                q18_frequency_o5_4 == 1 ~ "high",
                                q18_frequency_o6_5 == 1 ~ "high",
                                q18_frequency_o7_6 == 1 ~ "high",
                                q18_frequency_o8_7 == 1 ~ "high"),
         prior = as.factor(ifelse(q9_taking_into_account_esg_factors_o1_yes == 1, 1, 0)),
         ethnicity = case_when(q14_ethnicity_o1_white == 1 ~ "white",
                               q14_ethnicity_o2_asian ==1 ~ "asian",
                               q14_ethnicity_o3_hispanic == 1 ~ "hispanic",
                               q14_ethnicity_o4_african_american == 1 ~ "african american",
                               q14_ethnicity_o5_native_american ==1 ~ "native american",
                               q14_ethnicity_o6_other ==1 ~ "other"))

mean(dfcj$age, na.rm = T) # There are NAs

```

```{r}
dfcj =dfcj %>% 
  select(respondent_id,
         survey_id,
         choice_set,
         label,
         choice_indicator,
         expected_pension,
         firearms,
         fossil_fuels,
         may_employ_children,
         racial_diversity_mgmt,
         gender_equal_pay,
         respondent_length_of_interview_seconds,
         prior,
         income,
         gender,
         education,
         age,
         republican,
         state.weight,
         florida, 
         california,
         religiosity)
```

```{r}
dfcj = na.omit(dfcj)
```

```{r}

dfcj = dfcj %>% 
  mutate(age.cat = case_when(age > 17 & age <=24 ~ "18-24",
                             age >= 25 & age <=39 ~ "25-39",
                             age >= 40 & age <=55 ~ "40-55",
                             age >=56 ~ "56+"))

dfcj$age.cat <- factor(dfcj$age.cat, levels = c("18-24", "25-39", "40-55", "56+"))


```

there were some NAs!

```{r}
names(dfcj)
```

```{r}
# Assuming your data frame 'df' has 'gender', 'age', 'income', and 'education' columns

# Define the distributions
gender_dist <- c("male" = 44.5, "female" = 45.5, "other" = 10)

age_dist <- c("18-24" = 0.12, "25-39" = 0.27, "40-55" = 0.26, "56+" = 0.35)


income_dist <- c("under 15,000" = 8.3, "15,000 to 24,999" = 7.4, "25,000 to 34,999" = 7.6,
                 "35,000 to 49,999" = 10.6, "50,000 to 74,999" = 16.2, "75,000 to 99,999" = 12.3,
                 "100,000 or more" = 37.5)

                 
education_dist <- c("less than hs" = 9, "hs" = 28, "some college" = 15,
                    "college" = 33, "grad school" = 14)

# Normalize distributions to sum to 1 (100%)
gender_dist <- gender_dist / sum(gender_dist)
age_dist <- age_dist / sum(age_dist)
income_dist <- income_dist / sum(income_dist)
education_dist <- education_dist / sum(education_dist)
```

```{r}
median_complet_t = median(dfcj$respondent_length_of_interview_seconds)

dfcj = dfcj %>%
  filter(respondent_length_of_interview_seconds >= 0.5 * median_complet_t & respondent_length_of_interview_seconds <= 2 * median_complet_t)
```

```{r}
dfcj$gender <- factor(dfcj$gender, levels = c("male", "female", "other"))
dfcj$age.cat <- factor(dfcj$age.cat, levels = c("18-24", "25-39", "40-55", "56+"))
dfcj$income <- factor(dfcj$income, levels = c("15,000 to 24,999", "25,000 to 34,999",
                                               "35,000 to 49,999", "50,000 to 74,999", "75,000 to 99,999",
                                               "100,000 or more"))
dfcj$education <- factor(dfcj$education, levels = c("less than hs", "hs", "some college",
                                                     "college", "grad school"))

# Checking the levels of the income variable
levels(dfcj$income)

table(dfcj$income)


```

Mind around 25% of people reported income \>100K

```{r}

# Function to calculate weights for each row
calculate_weight <- function(data, column, dist) {
  factor_column <- factor(data[[column]], levels = names(dist))
  proportions <- table(factor_column) / nrow(data)

  # Handle NA values
  factor_column[is.na(factor_column)] <- "NA"
  proportions["NA"] <- 1

  weights <- vector("numeric", length = nrow(data))
  for (i in 1:nrow(data)) {
    cat <- as.character(factor_column[i])
    weights[i] <- dist[cat] / proportions[cat]
  }

  return(weights)
}

# Applying the function to each column
dfcj$gender_weight <- calculate_weight(dfcj, "gender", gender_dist)
dfcj$age_weight <- calculate_weight(dfcj, "age.cat", age_dist)
dfcj$income_weight <- calculate_weight(dfcj, "income", income_dist)
dfcj$education_weight <- calculate_weight(dfcj, "education", education_dist)

# View the first few entries

sum(is.na(dfcj$age_weight))
```

```{r}
dfcj$weights = dfcj$gender_weight * dfcj$age_weight * dfcj$income_weight * dfcj$education_weight * dfcj$state.weight

```

```{r}
summary(dfcj$weights)
```

```{r}
names(dfcj)
```

```{r}
library(ggthemes)
library(ggsci)
library(extrafont)
loadfonts()

amce1 = cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", weights = ~ weights)

amce1plot = plot(amce1, vline =0, feature_headers = F) +
  theme(text = element_text(family = "LM Roman 10")) +
scale_color_jco() 

amce1plot

ggsave(amce1plot, path = NULL, 
       filename = "amcecj1jmain.png",
       device = "png",
       type = "cairo", 
       dpi = "retina",
       width = 12, 
       height = 6)

```

Shorter amce df to produce smaller plot

```{r}
amce1shorter = amce1 %>% 
  filter(!str_detect(feature, "pension"))
#Trying to produce nicer plots

amce1shorter = plot(amce1shorter, vline =0, feature_headers = F) +
  theme(text = element_text(family = "LM Roman 10")) +
scale_color_jco() +
   ggplot2::facet_wrap(~feature, ncol = 1L,
                      scales = "free_y", strip.position = "top")

amce1shorter +
  ggplot2::scale_fill_manual(labels=c("firearms", "fossil fuels", "child labor", "racial diversity mgmt", "gender pay parity")) 
   


ggsave(amce1shorter, path = NULL, 
       filename = "amcecj1jmainb.png",
       device = "png",
       type = "cairo", 
       dpi = "retina", height = 4)

amce1shorter
```

The plot below displays the same result but distinguishing between respondents who identify as republicans and those that don't.

```{r echo=FALSE, warning=FALSE}
mmusw_by_r <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "mm", weights = ~ weights,
            by = ~republican)

amceusw_by_r <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", weights = ~ weights,
            by = ~republican)

plot(mmusw_by_r, group = "republican", vline = 0.5) +
  scale_colour_manual(na.translate = F, values = c("royalblue", "red3")) +
  ggtitle("U.S. Weighted Sample")

amce_byr_plot = plot(amceusw_by_r, group = "republican", vline = 0, feature_headers = F) +
  scale_colour_manual(na.translate = F, values = c("royalblue", "red3"), labels=c('no', 'yes')) +
    theme(text = element_text(family = "LM Roman 10"))

ggsave(amce_byr_plot, path = NULL, 
       filename = "amcecj1j_byr.png",
       device = "png",
       type = "cairo", 
       dpi = "retina")

amce_byr_plot

```

```{r}
amce_byr_shorter = amceusw_by_r %>% 
  filter(!str_detect(feature, "pension"))
#Trying to produce nicer plots

amce_byr_shorter_plot = plot(amce_byr_shorter, vline =0, feature_headers = F) +
  scale_colour_manual(na.translate = F, values = c("royalblue", "red3"), labels=c('no', 'yes')) +
    theme(text = element_text(family = "LM Roman 10")) +
   ggplot2::facet_wrap(~feature, ncol = 1L,
                      scales = "free_y", strip.position = "top")


ggsave(amce_byr_shorter_plot, path = NULL, 
       filename = "amce_byr_shorter.png",
       device = "png",
       type = "cairo", 
       dpi = "retina", height = 5)

amce_byr_shorter_plot
```

```{r}
diff_amces <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce_diff", weights = ~ weights,
            by = ~republican)

plot(diff_amces)

#plot(rbind(amceusw_by_w, diff_amces)) + ggplot2::facet_wrap(~BY, ncol = 3L) + theme_linedraw() + scale_color_jco()
```

```{r}
# Shorter plot easier to understand

amceusw_fl <- cj(dfcj, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", #weights = ~ weights,
            by = ~florida)

plot(amceusw_fl, group = "florida",vline=0) +
   scale_colour_manual(na.translate = F, values = c("royalblue", "orange3")) 
```

```{r}
table(dfcj$republican, dfcj$prior)
```

The first question asked whether people would like to restrict their investments to ESG-only alternatives. I coded the results as "prior." In principle, the choices of those who oppose ESG should show they are not influenced by environmental or social concerns. But this is not what the data show. Respondents with an anti-esg prior, are unaffected by the firearms feature. But they still favor options that ensure no children are employed and advocate for gender equality. They also tend to prefer investing in firms that advocate for racial diversity, but this effect is much smaller.

```{r echo=FALSE, warning=FALSE}
mmusw_byprior <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "mm", weights = ~ weights,
            by = ~prior)

amceusw_byprior <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", weights = ~ weights,
            by = ~prior)

plot(amceusw_byprior, group = "prior", vline = 0, feature_headers = F) +
  scale_colour_manual(na.translate = F, values = c("#F8867D", "#00BFC4"), labels=c('anti-ESG', 'pro-ESG')) + 
  theme(text = element_text(family = "LM Roman 10")) 
  

ggsave("amceprior.png",
       device = "png",
       type = "cairo", 
       dpi = "retina")

summary(amceusw_byprior)

# +
#  # scale_colour_manual(na.translate = F, values = c("navy", "turquoise")) +
#   ggtitle("U.S. Weighted Sample")
```

```{r}
#Check age differences

dfcj = dfcj %>% 
  mutate(fiftysix = factor(ifelse(age.cat == "56+", 1,0)))


amceusw_byage <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id,
            estimate = "amce", weights = ~ weights,
            by = ~fiftysix)

plot(amceusw_byage, group = "fiftysix", vline = 0, feature_headers = F)


# +
#   scale_colour_manual(na.translate = F, values = c("#F8867D", "#00BFC4"), labels=c('anti-ESG', 'pro-ESG')) + 
#   theme(text = element_text(family = "LM Roman 10")) 
  
```
```{r}
df56 = dfcj %>% 
  select(survey_id, fiftysix)

write.csv(df56, "df56.csv")
```


People in Florida are indifferent to environmental factors, but they are as pro-social as the U.S. and they care more about child labor than the U.S. average.

```{r echo=FALSE, warning=FALSE}
# Florida
amce_byfl <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~ survey_id, 
              estimate = "amce", 
              weights = ~weights,
              by = ~florida)

plot(amce_byfl, group = "florida", vline = 0) +
  scale_colour_manual(na.translate = F, values = c("royalblue", "red3")) 

ggsave("amcefl.pdf", width = 10, height = 5)
```

People's religiousness has a very minor effect. The more religious people are, the more they prefer investments that don't involve firearms.

# Religiosity

Religion just makes people more conservative

```{r echo=FALSE, warning=FALSE}
# calculate conditional MMs

dfcj = dfcj %>% 
  mutate(religiosity = factor(religiosity, 
                       levels = c("no/low", "mid", "high")))

dfcj$religiosity <- fct_relevel(dfcj$religiosity, "no/low", "mid","high")


amcesrel <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, 
               estimate = "amce", 
               by = ~religiosity)

diff_amcerel <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "amce_diff", 
    by = ~religiosity)


plot(diff_amcerel, vline=0) + ggplot2::facet_wrap(~BY, ncol = 3L) +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10")) 

#ggsave("amcerel.pdf", width = 10, height = 5)

#plot(rbind(mms, diff_mms)) + ggplot2::facet_wrap(~BY, ncol = 3L) #weird
```

Sanity check below: people closer to retirement are more sensible to changes in their expected pension. Interestingly, they value investments that don't involve firearms, unlike younger people.

```{r}

dfcjnr = dfcj %>% 
  filter(republican==0)

amcesrelnr <- cj(dfcjnr, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, 
               estimate = "amce", 
               by = ~religiosity)

diff_amcerelnr <- cj(dfcjnr, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "amce_diff", 
    by = ~religiosity)


plot(diff_amcerelnr, vline=0) + ggplot2::facet_wrap(~BY, ncol = 3L) +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10")) 
```

```{r}
#Only republicans

dfcjr = dfcj %>% 
  filter(republican==1)

amcesrelr <- cj(dfcjr, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, 
               estimate = "amce", 
               by = ~religiosity)

diff_amcerelr <- cj(dfcjr, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "amce_diff", 
    by = ~religiosity)


plot(diff_amcerelr, vline=0) + ggplot2::facet_wrap(~BY, ncol = 3L) +
  theme_classic() +
  theme(text = element_text(family = "LM Roman 10")) 
```


```{r echo=FALSE, warning=FALSE, width="7", height="5"}

mms_age <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, weights = ~weights, estimate = "mm", by = ~age.cat)

diff_mms_age <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, weights=~weights, estimate = "mm_diff", 
    by = ~age.cat)

plot(mms_age, vline = 0.5) + ggplot2::facet_wrap(~BY, ncol = 3L) + ggtitle("Marginal Means by Age")

#Now AMCE

amce_age <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, weights = ~weights, estimate = "amce", by = ~age.cat)

diff_amce_age <- cj(dfcj, choice_indicator ~ expected_pension + firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, weights=~weights, estimate = "amce_diff", 
    by = ~age.cat)

plot(amce_age, vline = 0) + ggplot2::facet_wrap(~BY, ncol = 3L) + ggtitle("AMCE by Age")

```

```{r}

dfcj.segments = dfcj %>% 
  select(survey_id, republican, prior, age.cat, education, gender)


write_csv(dfcj.segments, "dfcj_seg.csv")


```


```{r include=FALSE}
dfrep = dfcj %>% 
  filter(republican==1)
```

```{r}
dfnorep = dfcj %>% 
  filter(republican==0)
```

## Republicans' Religiousness doesn't make a difference

```{r echo=FALSE, warning=FALSE}
# calculate interaction AMCEs (ACIEs) 
#I changed to MM
amces_2 <- cj(dfrep, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm", by = ~religiosity)

diff_amces_2 <- cj(dfrep, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm_diff", by = ~religiosity)

plot(diff_amces_2, vline = 0) + ggplot2::facet_wrap(~BY, ncol = 3L) + ggtitle("Republicans Only: Religiosity")

#plot(rbind(amces_2, diff_amces_2)) + ggplot2::facet_wrap(~BY, ncol = 3L)
```

## Religiousness has a small effect in those who don't identify as republicans

Non-religious people oppose firearms and fossil fuels a tiny bit more than religious people.

```{r message=FALSE, warning=FALSE, include=FALSE}
mm_norep <- cj(dfnorep, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm", by = ~religiosity)

diff_mmnorep <- cj(dfnorep, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm_diff", by = ~religiosity)

plot(diff_mmnorep, vline = 0) + ggplot2::facet_wrap(~BY, ncol = 3L) + ggtitle("No Republicans Only: Religiosity")
```
Religion makes non-republicans more conservative


## Wealthier People tend to be less pro-social

```{r echo=FALSE, warning=FALSE}
mm_income <- cj(dfcj, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm", by = ~income)

diff_mm_income <- cj(dfcj, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "mm_diff", by = ~income)

plot(mm_income, vline = 0.5) + ggplot2::facet_wrap(~BY, ncol = 2L) + ggtitle("Marginal Means, U.S. by Income")

# plot(mm_income, vline = 0.5, group = "income_groups") +  ggtitle("Marginal Means, U.S. by Income")

amce_income <- cj(dfcj, choice_indicator ~ firearms + fossil_fuels + may_employ_children + racial_diversity_mgmt + gender_equal_pay, id = ~survey_id, estimate = "amce", by = ~income)

plot(amce_income, group = "income", vline = 0) + ggtitle("U.S. by Income (AMCE)")


```

```{r}
#demographics

cjmale = sum(dfcj$gender=="male")/24

cjfemale = sum(dfcj$gender=="female")/24

cjother = sum(dfcj$gender=="other")/24

age1 = mean(dfcj$age)

table(dfcj$income)
```

